Keystoneness, centrality, and the structural controllability of ecological networks

### 2019-01-13 paper/drafts_and_revisions/2019-01-14/supp-info.tex
Add revision with most responses to reviewers

The networks studied had species richness ranging between 19 and 87 when
considering only the largest component in each network). As shown by the
network asymmetry \emph{AS} (N. Blüthgen, Menzel, Hovestadt, Fiala, \&
Blüthgen, 2007), the networks had a low ratio of plants to pollinators
overall. Furthermore, the networks had relatively low levels of
nestedness (when measured using the quantitative version of the NODF
index; Almeida-Neto \& Ulrich, 2011). Details for each network can be
found in the Table \ref{tab:table-network-properties}.

@@

\caption{\label{tab:table-network-properties}Properties of the analysed plant-pollinator communities. Here show the number of species ($n_s$), the number of plants ($n_p$), the number of pollinators ($n_a$), the network connectance ($c$), the network asymmetry ($AS$), and the network nestedness (NODF index). All properties correspond to the network's largest component. British networks were assembled by Lopezaraiza-Mikel et al. (2007), Spanish were networks assembled by Bartomeus et al. (2008).}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{rlrrrrrrl}
\toprule
site & invader & $n_s$ & $n_p$ & $n_a$ & $c$ & $AS$ & NODF & location\\
\midrule
1 & — & 35 & 9 & 26 & 0.17 & -0.49 & 8.68 & Cap de Creus, Spain\\
1 & \textit{Carpobrotus affine} & 57 & 10 & 47 & 0.17 & -0.65 & 13.27 & Cap de Creus, Spain\\
\addlinespace
2 & — & 40 & 10 & 30 & 0.16 & -0.50 & 11.66 & Cap de Creus, Spain\\
2 & \textit{Carpobrotus affine} & 38 & 11 & 27 & 0.21 & -0.42 & 15.04 & Cap de Creus, Spain\\
\addlinespace
3 & — & 31 & 7 & 24 & 0.19 & -0.55 & 12.91 & Cap de Creus, Spain\\
3 & \textit{Opuntia stricta} & 33 & 8 & 25 & 0.18 & -0.52 & 9.96 & Cap de Creus, Spain\\
\addlinespace
4 & — & 35 & 10 & 25 & 0.17 & -0.43 & 12.43 & Cap de Creus, Spain\\
4 & \textit{Carpobrotus affine} & 57 & 14 & 43 & 0.14 & -0.51 & 13.70 & Cap de Creus, Spain\\
\addlinespace
5 & — & 35 & 8 & 27 & 0.19 & -0.54 & 11.91 & Cap de Creus, Spain\\
5 & \textit{Opuntia stricta} & 32 & 8 & 24 & 0.19 & -0.50 & 10.96 & Cap de Creus, Spain\\
\addlinespace
6 & — & 30 & 9 & 21 & 0.17 & -0.40 & 6.91 & Cap de Creus, Spain\\
6 & \textit{Opuntia stricta} & 37 & 9 & 28 & 0.17 & -0.51 & 12.45 & Cap de Creus, Spain\\
\addlinespace
7 & — & 37 & 6 & 31 & 0.19 & -0.68 & 18.33 & Bristol, United Kingdom\\
7 & \textit{Impatients grandulifera} & 57 & 8 & 49 & 0.20 & -0.72 & 14.36 & Bristol, United Kingdom\\
\addlinespace
8 & — & 48 & 5 & 43 & 0.21 & -0.79 & 5.87 & Bristol, United Kingdom\\
8 & \textit{Impatients grandulifera} & 87 & 15 & 72 & 0.11 & -0.66 & 8.12 & Bristol, United Kingdom\\
\addlinespace
9 & — & 55 & 12 & 43 & 0.13 & -0.56 & 13.01 & Bristol, United Kingdom\\
9 & \textit{Impatients grandulifera} & 86 & 11 & 75 & 0.13 & -0.74 & 13.40 & Bristol, United Kingdom\\
\addlinespace
10 & — & 19 & 3 & 16 & 0.38 & -0.68 & 9.99 & Bristol, United Kingdom\\
10 & \textit{Impatients grandulifera} & 54 & 6 & 48 & 0.21 & -0.78 & 7.56 & Bristol, United Kingdom\\
\bottomrule
\end{tabular}
\end{table}

@@

The algorithm implemented in \texttt{max\_bipartite\_matching}, however,
is only able to find \textbf{one} of possibly many maximum matchings in
a network. Though one maximum matching is enough to calculate
\emph{n\textsubscript{D}} and hence to provide an indication of the
manageability of a community, it is not sufficient to estimate the role
of individual species. To do that, we need to calculate all possible
maximum matchings. To do this, we again start from the alternative
bipartite representation in Figure
\ref{fig:fig-maximum-matching-procedure}b and assign an identity to each
of the links in the network. We will call this bipartite representation
\emph{P}. We then construct the line graph of the alternative bipartite
representation \emph{L(P)} (Figure \ref{fig:fig-all-maximum-matching}).
Each node in \emph{L(P)} represents a link in \emph{P} and these are
connected to each other if and only if they share a common node in
\emph{P}. We then calculate \emph{H}, the complement graph of
\emph{L(P)} and identify all of its maximal cliques (Figure
\ref{fig:fig-all-maximum-matching}). Here some extra definitions are
necessary. First, \emph{H} is a graph with the same nodes as \emph{L(P)}
but that has a link between two nodes if and only if there is not a link
in \emph{L(P)}. Second, a clique is a subset of nodes such that all
pairs of them are linked. Lastly, a maximal clique is a clique such that
there are no cliques composed of more nodes (Gutin, 2013). In this
example, there are two maximal cliques. The final step is then to map
these cliques onto the original network to obtain all possible maximal
cardinality matchings as shown in Figure
\ref{M-fig:fig-control-configuration} in the main text.

@@

The algorithm proposed by Zhang, Lv, \& Pu (2016) enable us to find all
minimum driver node sets without calculating all possible maximum
matchings. The algorithm is based on the construction of the input graph
of the directed network. Components in the input graph reveal the
correlations between nodes from a structural control perspective (Figure
\ref{fig:fig-input-graph}). The input graph is constructed based on the
\emph{control adjacency} of nodes in a maximum matching. Two nodes
\(x_i\) and \(x_j\) are said to be control adjacent if there is a node
\(x_k\) connecting \(x_i\) and \(x_j\) with an unmatched link
\(x_k-x_i\) and a matched link \(x_k-x_j\). For example \(a_1\) is
control adjacent to \(a_2\) in the top panel of Figure
\ref{fig:fig-input-graph}. If a node \(x_i\) is part of a minimum driver
node set then every node in the same component of \(x_i\) in the input
graph is a possible driver node.

@@

In order to calculate a node's control capacity \(\phi\), we harness the
fact that nodes can be classified into three groups according to their
role in the input graph. First, if \(x_i\) belongs to the minimum driver
node set and has no adjacent nodes, then it cannot be replaced and will
be part of every possible control configuration. Second, if \(x_i\) does
not belong to the minimum driver node set and is not adjacent to any
possible input node, then it does not part of the minimum driver node
set under any control configuration. Finally, if a node \(x_i\) belongs
to the minimum driver node set and is adjacent to another node \(x_j\)
in the input graph, then \(x_j\) must belong to another minimum driver
node to which \(x_i\) does not belong, in other words, \(x_i\) and
\(x_j\) are substitutable.

The first and the second group have a control capacity of \(\phi = 1\)
and \(\phi = 0\) respectively. Meanwhile, the third group has
intermediate values of control capacity which can be calculated by
computing the number of possible substitutions of a node by its control
adjacent nodes. As a rule of thumb, the largest the number of possible
substitutions an input node has, the smaller its control capacity.

@@

Our procedures to find minimum driver node sets are only adequate when
there are no reciprocal (bidirectional) links in the network. The
proportion of reciprocal links in relatively low. In fact, the
proportion of species pairs that are reciprocally connected in our
empirical networks is just 2.97\%. However, reciprocal links are not a
rare occurrence as 16 out of 20 empirical networks had at least one. To
calculate our controllability metrics at both the network (the relative
size of the minimum driver node set, \(n_D\)) and species level (control
capacity, \(\phi\), and the likelihood of being a superior node,
\(\sigma\)) we first need to generate all possible versions of the of
the network that include only non-reciprocal links (Figure
\ref{fig:fig-bidirectional}).

All of these non-reciprocal networks are as likely to be one that best
represents the superior/matched relationships in the network. As such,
we average the three metrics (\(n_D\), \(\phi\), and \(\sigma\)) across
all the networks without reciprocal links without weighting by the
number of possible control configurations.

@@

We follow R. P. Rohr, Saavedra, \& Bascompte (2014) and S. Saavedra,
Rohr, Olesen, \& Bascompte (2016) to calculate the structural stability
of the empirical networks. We first calculate the stability condition
\(\hat{\gamma}\) using all species in the network. To calculate the
contribution to stable coexistence of a given species, we removed the
focal species from the network and then calculated the corresponding
structural stability \(\Omega\) for a level of mutualism equal to the
stability condition found previously. For simplicity, in the main text
we show results for when there is a mutualistic trade-off of
\(\delta = 0\) and a mean interspecific competition of \(\rho = 0.01\)
(S. Saavedra et al., 2016). The choice of the parameters had only a
minor impact on the relative contribution of species to stable
coexistence (Figure \ref{fig:fig-rho-sensitivity}a) and overall there
was no change on our result that indicates that critical species (those
with \(\phi = 1\)) have a larger than average contribution to stable
coexistence (Figure \ref{fig:fig-rho-sensitivity}b).

@@

Visitation frequency has been shown to be an appropriate surrogate for
inter-specific effects in pollination networks (Bascompte, Jordano, \&
Olesen, 2006; Vázquez, Morris, \& Jordano, 2005). Nevertheless,
visitation is not equivalent to pollen deposition and might be
insufficient to reflect the dependences of plants on animals and vice
versa (Alarcón, 2010; King, Ballantyne, \& Willmer, 2013). We,
therefore, investigated the effect of calculating the dependences using
visitation or pollination effectiveness and importance---two metrics
more proximate to plant reproductive success. We did this by comparing
\emph{(i)} the size of the minimum driver node set \(n_D\) of the
community, \emph{(ii)} the species' control capacity and, \emph{(iii)}
the species' probability of being a superior node. To do this, we used
data collected by G. Ballantyne, Baldock, \& Willmer (2015) from a low
diversity pollination community at a dry lowland heathland in Dorset, UK
(50° 43.7'N 2° 07.2'W). First, deposition networks were quantified using
the mean single visit deposition---the number of conspecific pollen
grains effectively deposited on a virgin stigma during a single visit by
a particular animal (G. Ballantyne et al., 2015; King et al., 2013;
Ne'eman, Jürgens, Newstrom-Lloyd, Potts, \& Dafni, 2009). Second,
visitation networks were constructed by counting the visits to flowers
during Single Visit Depositions. Finally, pollinator importance networks
were constructed as the product of pollinator efficiency and visit
frequency.

At a network scale the driver-node density \(n_D\) was consistent among
the three weighting schemes (0.67 for deposition, 0.67 for the
visitation, and 0.62 for the pollinator-importance network,
respectively). The choice of weighting can also have an impact on at the
species level. Therefore we calculated \(\phi\) and \(\sigma\) and
calculated it's correlation among all three weighting schemes. Although
visitation and efficiency (pollen deposition) produce moderately
different results, we found a very strong agreement between the order
produced by visitation and importance which is arguably a more accurate
metric of interspecific effects (Table
\ref{tab:tab-assumption-visitation}).

@@

To do so we removed a portion of the visits, for each network, and
calculated how three control metrics of the subsampled network compare
to those of the full network. Specifically, we calculated the difference
between the relative size of the minimum driver node set \(n_D\) of the
subsampled and the full network, the Spearman correlation between the
control capacities \(\phi\) and the probability of being a superior node
\(\sigma\) that were obtained for the empirical network and subsamples
of it. Finally, we also compared the control capacity of critical
species (\(\phi=1\)) across the different subsamples. We removed up to
20\% of the interactions in 1\% increments. We repeated the procedure
for each network to obtain a total sample size of \(n=400\).

Overall, the results of the sensitivity analysis indicate that our
approach is likely to still be useful in the absence of complete
sampling. Specifically, as the proportion of sampled interaction
decreased, the variability of \(n_D\) increased but was overall similar
to that obtained when using all available interactions (Figure
\ref{fig:fig-assumption-sampling-nd}). Similarly, the correlation
between \(\phi\) and \(\sigma\) of empirical and subsampled networks was
high even for extreme levels of undersampling (Figure
\ref{fig:fig-assumption-sampling-cor}). Importantly, critical species in
the empirical networks were also critical species in the subsampled
networks in a large majority of cases (Figure
\ref{fig:fig-assumption-sampling-crit}).

@@

\caption{\label{tab:tab-controllability-model-results}Model selection table based on the Akaike Information Criterion for small samples for candidate models of size of the minimum driver node set ($n_D$) in the empirical networks. There was no evidence for any of the evaluated predictors: the invasion status (inv), the network connectance (c), the network nestedness (NODF) the number of species ($n_S$) the network asymmetry ($AS_s$) or the interaction strength asymmetry ($AS_s$). Only candidate models with a weight $>0.01$ are shown.}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{rrrlrlrrrrr}
\toprule
(Intercept) & C & $AS_s$ & inv & $n_s$ & study & $AS_n$ & NODF & df & delta & weight\\
\midrule
0.89 & -0.40 & --- & --- & -0.20 & --- & -0.50 & -0.19 & 6 & 0.00 & 0.21\\
1.07 & --- & -0.11 & --- & --- & --- & -0.31 & --- & 4 & 1.33 & 0.11\\
0.95 & -0.38 & --- & --- & -0.20 & --- & -0.50 & --- & 5 & 1.46 & 0.10\\
1.03 & --- & -0.10 & --- & --- & --- & -0.31 & -0.15 & 5 & 2.23 & 0.07\\
0.84 & -0.42 & --- & --- & -0.22 & + & -0.46 & -0.20 & 7 & 2.91 & 0.05\\
1.02 & -0.11 & -0.13 & --- & --- & --- & -0.31 & --- & 5 & 2.91 & 0.05\\
0.98 & -0.11 & -0.12 & --- & --- & --- & -0.31 & -0.16 & 6 & 3.66 & 0.03\\
1.07 & --- & --- & --- & --- & --- & -0.38 & --- & 3 & 3.79 & 0.03\\
1.02 & --- & --- & --- & --- & --- & -0.38 & -0.18 & 4 & 3.90 & 0.03\\
0.91 & -0.34 & -0.04 & --- & -0.16 & --- & -0.45 & -0.18 & 7 & 4.09 & 0.03\\
0.97 & -0.30 & -0.06 & --- & -0.14 & --- & -0.43 & --- & 6 & 4.32 & 0.02\\
0.90 & -0.40 & --- & --- & -0.21 & + & -0.47 & --- & 6 & 4.43 & 0.02\\
0.88 & -0.41 & --- & + & -0.21 & --- & -0.51 & -0.20 & 7 & 4.65 & 0.02\\
1.06 & --- & -0.12 & --- & 0.02 & --- & -0.29 & --- & 5 & 4.75 & 0.02\\
1.07 & --- & -0.11 & + & --- & --- & -0.31 & --- & 5 & 4.93 & 0.02\\
1.07 & --- & -0.11 & --- & --- & + & -0.31 & --- & 5 & 4.95 & 0.02\\
0.95 & -0.38 & --- & + & -0.20 & --- & -0.51 & --- & 6 & 5.62 & 0.01\\
1.08 & --- & --- & --- & -0.04 & --- & -0.40 & --- & 4 & 5.97 & 0.01\\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{figure}
\centering
\includegraphics{/Users/efc29/github/driver-species/paper/supp-info_files/figure-latex/fig-correlogram-1.pdf}
\caption{\label{fig:fig-correlogram}Mean Spearman correlation coefficients
between control metrics (control capcity \(\phi\) and the likelyhood of
being a superior node \(\sigma\)) and centrality metrics commonly used
to estimate a species' `keystoness' (closeness centrality \(l\) ,
betwenness \(w\), eigen centrality \(e\), page rank \(g\) and degre
\(k\)) in each of the networks. Purple and orange tiles indicate a
positive correlation or negative correlation respectively.}
\end{figure}

@@

\hypertarget{ref-ballantyne_constructing_2015}{}
Ballantyne, G., Baldock, K. C. R., \& Willmer, P. G. (2015).
Constructing more informative plantPollinator networks: Visitation and
pollen deposition networks in a heathland plant community.
\emph{Proceedings of the Royal Society B: Biological Sciences},
\emph{282}(1814), 20151130.
doi:\href{https://doi.org/10.1098/rspb.2015.1130}{10.1098/rspb.2015.1130}

@@

\hypertarget{ref-neeman_framework_2009}{}
Ne'eman, G., Jürgens, A., Newstrom-Lloyd, L., Potts, S. G., \& Dafni, A.
(2009). A framework for comparing pollinator performance: Effectiveness
and efficiency. \emph{Biological Reviews}, no--no.
doi:\href{https://doi.org/10.1111/j.1469-185X.2009.00108.x}{10.1111/j.1469-185X.2009.00108.x}

>>>>

The networks studied had species richness ranging between 19 and 87
(when considering only the largest component in each network). As shown
by the network asymmetry \emph{AS} (N. Blüthgen, Menzel, Hovestadt,
Fiala, \& Blüthgen, 2007), the networks had a low ratio of plants to
pollinators overall. Furthermore, the networks had relatively low levels
of nestedness (when measured using the quantitative version of the NODF
index; Almeida-Neto \& Ulrich, 2011). Details for each network can be
found in the Table \ref{tab:table-network-properties}.

@@

\caption{\label{tab:table-network-properties}Properties of the analysed plant-pollinator communities. Here show the number of species ($n_s$), the number of plants ($n_p$), the number of pollinators ($n_a$), the network connectance ($C$), the network asymmetry ($AS$), and the network nestedness (NODF index). All properties correspond to the network's largest component. British networks were assembled by Lopezaraiza-Mikel et al. (2007), Spanish were networks assembled by Bartomeus et al. (2008).}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{rlrrrrrrl}
\toprule
site & invader & $n_s$ & $n_p$ & $n_a$ & $c$ & $AS$ & NODF & location\\
\midrule
1 & — & 35 & 9 & 26 & 0.17 & -0.49 & 8.68 & Cap de Creus, Spain\\
1 & \textit{Carpobrotus affine} & 57 & 10 & 47 & 0.17 & -0.65 & 13.27 & Cap de Creus, Spain\\
\addlinespace
2 & — & 40 & 10 & 30 & 0.16 & -0.50 & 11.66 & Cap de Creus, Spain\\
2 & \textit{Carpobrotus affine} & 38 & 11 & 27 & 0.21 & -0.42 & 15.04 & Cap de Creus, Spain\\
\addlinespace
3 & — & 31 & 7 & 24 & 0.19 & -0.55 & 12.91 & Cap de Creus, Spain\\
3 & \textit{Opuntia stricta} & 33 & 8 & 25 & 0.18 & -0.52 & 9.96 & Cap de Creus, Spain\\
\addlinespace
4 & — & 35 & 10 & 25 & 0.17 & -0.43 & 12.43 & Cap de Creus, Spain\\
4 & \textit{Carpobrotus affine} & 57 & 14 & 43 & 0.14 & -0.51 & 13.70 & Cap de Creus, Spain\\
\addlinespace
5 & — & 35 & 8 & 27 & 0.19 & -0.54 & 11.91 & Cap de Creus, Spain\\
5 & \textit{Opuntia stricta} & 32 & 8 & 24 & 0.19 & -0.50 & 10.96 & Cap de Creus, Spain\\
\addlinespace
6 & — & 30 & 9 & 21 & 0.17 & -0.40 & 6.91 & Cap de Creus, Spain\\
6 & \textit{Opuntia stricta} & 37 & 9 & 28 & 0.17 & -0.51 & 12.45 & Cap de Creus, Spain\\
\addlinespace
7 & — & 37 & 6 & 31 & 0.19 & -0.68 & 18.33 & Bristol, United Kingdom\\
7 & \textit{Impatients grandulifera} & 57 & 8 & 49 & 0.20 & -0.72 & 14.36 & Bristol, United Kingdom\\
\addlinespace
8 & — & 48 & 5 & 43 & 0.21 & -0.79 & 5.87 & Bristol, United Kingdom\\
8 & \textit{Impatients grandulifera} & 87 & 15 & 72 & 0.11 & -0.66 & 8.12 & Bristol, United Kingdom\\
\addlinespace
9 & — & 55 & 12 & 43 & 0.13 & -0.56 & 13.01 & Bristol, United Kingdom\\
9 & \textit{Impatients grandulifera} & 86 & 11 & 75 & 0.13 & -0.74 & 13.40 & Bristol, United Kingdom\\
\addlinespace
10 & — & 19 & 3 & 16 & 0.38 & -0.68 & 9.99 & Bristol, United Kingdom\\
10 & \textit{Impatients grandulifera} & 54 & 6 & 48 & 0.21 & -0.78 & 7.56 & Bristol, United Kingdom\\
\bottomrule
\end{tabular}
\end{table}

@@

The algorithm implemented in \texttt{max\_bipartite\_matching}, however,
is only able to find \textbf{one} of possibly many maximum matchings in
a network. Though one maximum matching is enough to calculate
\emph{n\textsubscript{D}} and hence to provide an indication of the
manageability of a community, it is not sufficient to estimate the role
of individual species. To do that, we need to calculate all possible
maximum matchings. To do this, we again start from the alternative
bipartite representation in Figure
\ref{fig:fig-maximum-matching-procedure} (center panel) and assign an
identity to each of the links in the network. We will call this
bipartite representation \emph{P}. We then construct the line graph of
the alternative bipartite representation \emph{L(P)} (Figure
\ref{fig:fig-all-maximum-matching}). Each node in \emph{L(P)} represents
a link in \emph{P} and these are connected to each other if and only if
they share a common node in \emph{P}. We then calculate \emph{H}, the
complement graph of \emph{L(P)} and identify all of its maximal cliques
(Figure \ref{fig:fig-all-maximum-matching}). Here some extra definitions
are necessary. First, \emph{H} is a graph with the same nodes as
\emph{L(P)} but that has a link between two nodes if and only if there
is not a link in \emph{L(P)}. Second, a clique is a subset of nodes such
that all pairs of them are linked. Lastly, a maximal clique is a clique
such that there are no cliques composed of more nodes (Gutin, 2013). In
this example, there are two maximal cliques. The final step is then to
map these cliques onto the original network to obtain all possible
maximal cardinality matchings as shown in Figure
\ref{M-fig:fig-control-configuration} in the main text.

@@

The algorithm proposed by Zhang, Lv, \& Pu (2016) enables us to find all
minimum driver node sets without calculating all possible maximum
matchings. The algorithm is based on the construction of the input graph
of the directed network. Components in the input graph reveal the
correlations between nodes from a structural control perspective (Figure
\ref{fig:fig-input-graph}). The input graph is constructed based on the
\emph{control adjacency} of nodes in a maximum matching. Two nodes
\(x_i\) and \(x_j\) are said to be control adjacent if there is a node
\(x_k\) connecting \(x_i\) and \(x_j\) with an unmatched link
\(x_k-x_i\) and a matched link \(x_k-x_j\). For example \(a_1\) is
control adjacent to \(a_2\) in the top panel of Figure
\ref{fig:fig-input-graph}. If a node \(x_i\) is part of a minimum driver
node set then every node in the same component of \(x_i\) in the input
graph is a possible driver node.

@@

In order to calculate a node's control capacity \(\phi\), we harness the
fact that nodes can be classified into three groups according to their
role in the input graph. First, if \(x_i\) belongs to the minimum driver
node set and has no adjacent nodes, then it cannot be replaced and will
be part of every possible control configuration. Second, if \(x_i\) does
not belong to the minimum driver node set and is not adjacent to any
possible input node, then it does not become part of the minimum driver
node set under any control configuration. Finally, if a node \(x_i\)
belongs to the minimum driver node set and is adjacent to another node
\(x_j\) in the input graph, then \(x_j\) must belong to another minimum
driver node to which \(x_i\) does not belong, in other words, \(x_i\)
and \(x_j\) are substitutable.

The first and the second group have a control capacity of \(\phi = 1\)
and \(\phi = 0\) respectively. Meanwhile, the third group has
intermediate values of control capacity which can be calculated by
computing the number of possible substitutions of a node by its control
adjacent nodes. As a rule of thumb, the larger the number of possible
substitutions an input node has, the smaller its control capacity.

@@

Our procedures to find minimum driver node sets are only adequate when
there are no reciprocal (bidirectional) links in the network. The
proportion of reciprocal links in relatively low. In fact, the
proportion of species pairs that are reciprocally connected in our
empirical networks is just 2.97\%. However, reciprocal links are not a
rare occurrence as 16 out of 20 empirical networks had at least one. To
calculate our controllability metrics at both the network (the relative
size of the minimum driver node set, \(n_D\)) and species level (control
capacity, \(\phi\), and wether it is a superior node, \(\sigma\)) we
first need to generate all possible versions of the of the network that
include only non-reciprocal links (Figure \ref{fig:fig-bidirectional}).

All of these non-reciprocal networks are as likely to be one that best
represents the superior/matched relationships in the network. As such,
we average the three metrics (\(n_D\), \(\phi\), and \(\sigma\)) across
all the networks without reciprocal links without weighting by the
number of possible control configurations. It is important to note that
a species that is found to be a superior node under a particular control
configuration, will be so in all possible control configurations for the
particular non-reciprocal network. We, therefore denote the average of
\(\sigma\) across all non-reciprocal versions as the probability of the
species being a superior node in its community.

@@

We follow Rohr, Saavedra, \& Bascompte (2014) and Saavedra, Rohr,
Olesen, \& Bascompte (2016) to calculate the structural stability of the
empirical networks. We first calculate the stability condition
\(\hat{\gamma}\) using all species in the network. To calculate the
contribution to stable coexistence of a given species, we removed the
focal species from the network and then calculated the corresponding
structural stability \(\Omega\) for a level of mutualism equal to the
stability condition found previously. For simplicity, in the main text
we show results for when there is a mutualistic trade-off of
\(\delta = 0\) and a mean interspecific competition of \(\rho = 0.01\)
(Saavedra et al., 2016). The choice of the parameters had only a minor
impact on the relative contribution of species to stable coexistence
(Figure \ref{fig:fig-rho-sensitivity}a) and overall there was no change
on our result that indicates that critical species (those with
\(\phi = 1\)) have a larger than average contribution to stable
coexistence (Figure \ref{fig:fig-rho-sensitivity}b).

@@

Visitation frequency has been shown to be an appropriate surrogate for
inter-specific effects in pollination networks (Bascompte, Jordano, \&
Olesen, 2006; Vázquez, Morris, \& Jordano, 2005). Nevertheless,
visitation is not equivalent to pollen deposition and might be
insufficient to reflect the dependences of plants on animals and vice
versa (Alarcón, 2010; King, Ballantyne, \& Willmer, 2013). We,
therefore, investigated the effect of calculating the dependences using
visitation or pollination effectiveness and importance---two metrics
more proximate to plant reproductive success. We did this by comparing
\emph{(i)} the size of the minimum driver node set \(n_D\) of the
community, \emph{(ii)} the species' control capacity and, \emph{(iii)}
the species' probability of being a superior node. To do this, we used
data collected by G. Ballantyne, Baldock, \& Willmer (2015) from a low
diversity pollination community at a dry lowland heathland in Dorset, UK
(50° 43.7'N 2° 07.2'W). First, deposition networks were quantified using
the mean single visit deposition---the number of conspecific pollen
grains effectively deposited on a virgin stigma during a single visit by
a particular animal (G. Ballantyne et al., 2015; King et al., 2013;
Ne'eman, Jürgens, Newstrom-Lloyd, Potts, \& Dafni, 2010). Second,
visitation networks were constructed by counting the visits to flowers
during Single Visit Depositions. Finally, pollinator importance networks
were constructed as the product of pollinator efficiency and visit
frequency.

At a network scale the size of the minimum driver node set \(n_D\) was
consistent among the three weighting schemes (0.67 for deposition, 0.67
for the visitation, and 0.62 for the pollinator-importance network,
respectively). The choice of weighting can also have an impact on at the
species level. Therefore we calculated \(\phi\) and \(\sigma\) and
calculated its correlation among all three weighting schemes. Although
visitation and efficiency (pollen deposition) produce moderately
different results, we found a very strong agreement between the order
produced by visitation and importance which is arguably a more accurate
metric of interspecific effects (Table
\ref{tab:tab-assumption-visitation}).

@@

To do so, we removed a portion of the visits, for each network, and
calculated how three control metrics of the subsampled network compare
to those of the full network. Specifically, we calculated the difference
between the relative size of the minimum driver node set \(n_D\) of the
subsampled and the full network, the Spearman correlation between the
control capacities \(\phi\) and the probability of being a superior node
\(\sigma\) that were obtained for the empirical network and subsamples
of it. Finally, we also compared the control capacity of critical
species (\(\phi=1\)) across the different subsamples. We removed up to
20\% of the interactions in 1\% increments. We repeated the procedure
for each network to obtain a total sample size of \(n=400\).

Overall, the results of the sensitivity analysis indicate that our
approach is likely to still be useful in the absence of complete
sampling. Specifically, as the proportion of sampled interactions
decreased, the variability of \(n_D\) increased but was overall similar
to that obtained when using all available interactions (Figure
\ref{fig:fig-assumption-sampling-nd}). Similarly, the correlation
between \(\phi\) and \(\sigma\) of empirical and subsampled networks was
high even for extreme levels of undersampling (Figure
\ref{fig:fig-assumption-sampling-cor}). Importantly, critical species in
the empirical networks were also critical species in the subsampled
networks in a large majority of cases (Figure
\ref{fig:fig-assumption-sampling-crit}).

@@

\caption{\label{tab:tab-controllability-model-results}Model selection table based on the Akaike Information Criterion for small samples for candidate models of size of the minimum driver node set ($n_D$) in the empirical networks. The evaluated variables are: the invasion status (inv), the network connectance ($C$), the network nestedness (NODF) the number of species ($n_S$) the network asymmetry ($AS_s$) or the interaction strength asymmetry ($AS_s$). Only candidate models with a weight $>0.01$ are shown.}
\centering
\fontsize{8}{10}\selectfont
\begin{tabular}[t]{rrrlrlrrrrr}
\toprule
(Intercept) & C & $AS_s$ & inv & $n_s$ & study & $AS_n$ & NODF & df & delta & weight\\
\midrule
0.89 & -0.40 & --- & --- & -0.20 & --- & -0.50 & -0.19 & 6 & 0.00 & 0.21\\
1.07 & --- & -0.11 & --- & --- & --- & -0.31 & --- & 4 & 1.33 & 0.11\\
0.95 & -0.38 & --- & --- & -0.20 & --- & -0.50 & --- & 5 & 1.46 & 0.10\\
1.03 & --- & -0.10 & --- & --- & --- & -0.31 & -0.15 & 5 & 2.23 & 0.07\\
0.84 & -0.42 & --- & --- & -0.22 & + & -0.46 & -0.20 & 7 & 2.91 & 0.05\\
1.02 & -0.11 & -0.13 & --- & --- & --- & -0.31 & --- & 5 & 2.91 & 0.05\\
0.98 & -0.11 & -0.12 & --- & --- & --- & -0.31 & -0.16 & 6 & 3.66 & 0.03\\
1.07 & --- & --- & --- & --- & --- & -0.38 & --- & 3 & 3.79 & 0.03\\
1.02 & --- & --- & --- & --- & --- & -0.38 & -0.18 & 4 & 3.90 & 0.03\\
0.91 & -0.34 & -0.04 & --- & -0.16 & --- & -0.45 & -0.18 & 7 & 4.09 & 0.03\\
0.97 & -0.30 & -0.06 & --- & -0.14 & --- & -0.43 & --- & 6 & 4.32 & 0.02\\
0.90 & -0.40 & --- & --- & -0.21 & + & -0.47 & --- & 6 & 4.43 & 0.02\\
0.88 & -0.41 & --- & + & -0.21 & --- & -0.51 & -0.20 & 7 & 4.65 & 0.02\\
1.06 & --- & -0.12 & --- & 0.02 & --- & -0.29 & --- & 5 & 4.75 & 0.02\\
1.07 & --- & -0.11 & + & --- & --- & -0.31 & --- & 5 & 4.93 & 0.02\\
1.07 & --- & -0.11 & --- & --- & + & -0.31 & --- & 5 & 4.95 & 0.02\\
0.95 & -0.38 & --- & + & -0.20 & --- & -0.51 & --- & 6 & 5.62 & 0.01\\
1.08 & --- & --- & --- & -0.04 & --- & -0.40 & --- & 4 & 5.97 & 0.01\\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{figure}
\centering
\includegraphics{/Users/efc29/github/driver-species/paper/supp-info_files/figure-latex/fig-correlogram-1.pdf}
\caption{\label{fig:fig-correlogram}Mean Spearman correlation coefficients
between control metrics (control capcity \(\phi\) and the likelihood of
being a superior node \(\sigma\)) and centrality metrics commonly used
to estimate a species' `keystoness' (closeness centrality \(l\) ,
betwenness \(w\), eigen centrality \(e\), page rank \(g\) and degre
\(k\)) in each of the networks. Purple and orange tiles indicate a
positive correlation or negative correlation respectively.}
\end{figure}

@@

\hypertarget{ref-ballantyne_constructing_2015}{}
Ballantyne, G., Baldock, K. C. R., \& Willmer, P. G. (2015).
Constructing more informative plant-pollinator networks: Visitation and
pollen deposition networks in a heathland plant community.
\emph{Proceedings of the Royal Society B: Biological Sciences},
\emph{282}(1814), 20151130.
doi:\href{https://doi.org/10.1098/rspb.2015.1130}{10.1098/rspb.2015.1130}

@@

\hypertarget{ref-neeman_framework_2010}{}
Ne'eman, G., Jürgens, A., Newstrom-Lloyd, L., Potts, S. G., \& Dafni, A.
(2010). A framework for comparing pollinator performance: Effectiveness
and efficiency. \emph{Biological Reviews}, no--no.
doi:\href{https://doi.org/10.1111/j.1469-185X.2009.00108.x}{10.1111/j.1469-185X.2009.00108.x}
